---
title: "twitter markdown practice"
author: "Michael Warner"
date: "January 10, 2018"
output: html_document
---

It's been awhile since I've done anything in R and so to get back in the habit I started playing around a bit.  I already had twitter api access from a few years back so decided to call up some tweets, run some analysis, create some visualizations, all while learning and becoming more familiar with creating rmarkdown documents.

To begin I needed to pull up some of the required libaries.

```{r}
library(twitteR)
library(tm)
library(wordcloud)
```

Then I needed to setup authentication with the twitter api.

```{r, echo = FALSE}
consumer_key <- "MwzdnvR6pV6bAbOPJ5iVMrUxx"
consumer_secret <- "rkBB6ShG8azc9qzUtDmboRZMDlnuZdNaElCHFKFS583quyX4tC"
access_token <- "1568356658-hF0Y3ts1OGEyPssL456qwpMvB9A4kEX6KrCQ1Od"
access_secret <- "3ZmwbFUlYYmCm6b0byP0OX1fEEFhxqi2V2EIOyOnzPC6U"
```


```{r}
setup_twitter_oauth(consumer_key, consumer_secret, access_token, access_secret)
```

So I called for some user timeline info from a few different users through the twitter api.

```{r}
tweets <- userTimeline("DailyZen", n = 3200)
tweets_text <- sapply(tweets, function(x) x$getText())
zen_corpus <- Corpus(VectorSource(tweets_text))
```

```{r}
zen_clean <- tm_map(zen_corpus, removePunctuation)
zen_clean2 <- tm_map(zen_clean, content_transformer(tolower))
zen_clean3 <- tm_map(zen_clean2, removeWords, stopwords("english"))
zen_clean4 <- tm_map(zen_clean3, removeNumbers)
zen_clean5 <- tm_map(zen_clean4, stripWhitespace)
```

```{r}
wordcloud(zen_clean5, random.order = F, scale = c(2, 0.25), colors = rainbow(50))
```
Of course a timeline full of buddhist, zen monk quotes talks about life and things alot.  And interestingly the words *can* and *will* come up alot from the tweets pulled.  So *can* I do something (like meditate, study, read, etc., yeah), but *will* I do something now that remains to be seen.
```{r}
warren <- userTimeline("elizabethwarren", n = 3200)
```

```{r echo = FALSE}
warren_tweets <- sapply(warren, function(x) x$getText())
warren_corpus <- Corpus(VectorSource(warren_tweets))
```

```{r echo = FALSE}
warren_clean <- tm_map(warren_corpus, removePunctuation)
warren_clean2 <- tm_map(warren_clean, content_transformer(tolower))
warren_clean3 <- tm_map(warren_clean2, removeWords, stopwords("english"))
warren_clean4 <- tm_map(warren_clean3, removeNumbers)
warren_clean5 <- tm_map(warren_clean4, stripWhitespace)
```

```{r echo = FALSE}
wordcloud(warren_clean5, random.order = F, scale = c(2, 0.25), colors = rainbow(50))
```
It is somewhat interesting in the few tweets that a pulled from Senator Elizabeth Warren's timeline is talks about herself alot presumably but of course she could be referencing other Elizabeth's and/or Warren's.
```{r}
paul <- userTimeline("randpaul", n = 3200)
```

```{r echo = FALSE}
paul_tweets <- sapply(paul, function(x) x$getText())
paul_corpus <- Corpus(VectorSource(paul_tweets))
```

```{r echo = FALSE}
paul_clean <- tm_map(paul_corpus, removePunctuation)
paul_clean2 <- tm_map(paul_clean, content_transformer(tolower))
paul_clean3 <- tm_map(paul_clean2, removeWords, stopwords("english"))
paul_clean4 <- tm_map(paul_clean3,  removeNumbers)
paul_clean5 <- tm_map(paul_clean4, stripWhitespace)
```

```{r echo = FALSE}
wordcloud(paul_clean5, random.order = F, scale = c(2, 0.25), colors = rainbow(50))
```
Senator Paul Rand on the other hand referneces government, bill's, #airingofgrievances, and some current events.  Also he seemed to reference the Seinfeld show holiday Festivus.  Which should always be seen as a plus because it's a holiday for the rest of us!
